Hydra Battles and Cie

### 2020-12-31 doc/part-hydras.tex
minor modifications

The following class specifies a strict inclusion of segments. The notation \texttt{OA} describes a segment $[0,\alpha($, and \texttt{OB} is a larger segment (which contains a notation for $\alpha$, whilst $\alpha$ is not represented in \texttt{OA}). We require also  that the comparison functions of the two notation systems are compatible.

@@

\begin{Coqsrc}
Class ON_correct `(alpha : Schutte_basics.Ord)
     `(OA : @ON A ltA  compareA)
      (iota : A -> Schutte_basics.Ord) :=
  { ON_correct_inj : forall a, Schutte_basics.lt (iota a) alpha;
    ON_correct_onto : forall beta, Schutte_basics.lt beta alpha ->
                                exists b, iota b = beta;
    On_compare_spec : forall a b:A,
        match compareA a b with
          Datatypes.Lt => Schutte_basics.lt (iota a) (iota b)
        | Datatypes.Eq => iota a = iota b
        | Datatypes.Gt => Schutte_basics.lt (iota b) (iota a)
        end}.
\end{Coqsrc}

@@

\label{types:ON-iso} 
\begin{Coqsrc}
Class  ON_Iso 
       `(OA : @ON A ltA compareA)
       `(OB : @ON B ltB  compareB)
       (f : A -> B)
       (g : B -> A):=
  {
  iso_compare: forall x y : A, 
      compareB (f x) (f y) = compareA x y;
  iso_inv1 : forall a, g (f a)= a;
  iso_inv2 : forall b, f (g b) = b}.
\end{Coqsrc}

@@

\begin{exercise}
Let $i$ be some natural number. Prove that the notation systems 
\texttt{Omega} and (\texttt{ON\_plus (OrdFin $i$) Omega}) are isomorphic.

{\it \textbf{Note:} This property reflects the equality $i+\omega=\omega$, that we prove also in larger notation systems, as well as in Schütte's model.}

This exercise is partially solved for $i=3$ (in ~\href{../theories/html/hydras.OrdinalNotations.Example_3PlusOmega.html}{OrdinalNotations.Example\_3PlusOmega}).

@@

Prove formally  that \texttt{ON\_mult (FinOrd $i$) Omega} is isomorphic to
\texttt{Omega}  whilst
\texttt{Omega}  is a sub-notation of \texttt{ON\_mult Omega (FinOrd $i$)},
for any strictly positive $i$.
\end{project}

>>>>

The following class specifies a strict inclusion of segments. The notation \texttt{OA} describes a segment $[0,\alpha)$, and \texttt{OB} is a larger segment (which contains a notation for $\alpha$, whilst $\alpha$ is not represented in \texttt{OA}). We require also  that the comparison functions of the two notation systems are compatible.

@@

\begin{Coqsrc}
Class ON_correct `(alpha : Schutte_basics.Ord)
     `(OA : @ON A ltA  compareA)
      (iota : A -> Schutte_basics.Ord) :=
  { ON_correct_inj : forall a, Schutte_basics.lt (iota a) alpha;
    ON_correct_onto : forall beta, Schutte_basics.lt beta alpha ->
                                exists b, iota b = beta;
    On_compare_spec : forall a b:A,
        match compareA a b with
          Datatypes.Lt => Schutte_basics.lt (iota a) (iota b)
        | Datatypes.Eq => iota a = iota b
        | Datatypes.Gt => Schutte_basics.lt (iota b) (iota a)
        end
}.
\end{Coqsrc}

@@

\label{types:ON-iso} 
\begin{Coqsrc}
Class  ON_Iso 
       `(OA : @ON A ltA compareA)
       `(OB : @ON B ltB  compareB)
       (f : A -> B)
       (g : B -> A):=
  {
  iso_compare: forall x y : A, 
      compareB (f x) (f y) = compareA x y;
  iso_inv1 : forall a, g (f a)= a;
  iso_inv2 : forall b, f (g b) = b
}.
\end{Coqsrc}

@@

\begin{exercise}
\label{exo:i-plus-omega}
Let $i$ be some natural number. Prove that the notation systems 
\texttt{Omega} and (\texttt{ON\_plus (OrdFin $i$) Omega}) are isomorphic.

{\it \textbf{Note:} This property reflects the equality $i+\omega=\omega$, that we prove also in larger notation systems, as well as in Schütte's model.}
This exercise is partially solved for $i=3$ (in ~\href{../theories/html/hydras.OrdinalNotations.Example_3PlusOmega.html}{OrdinalNotations.Example\_3PlusOmega}).

@@

Prove formally  that \texttt{ON\_mult (FinOrd $i$) Omega} is isomorphic to
\texttt{Omega}  whilst
\texttt{Omega}  is a sub-notation of \texttt{ON\_mult Omega (FinOrd $i$)},
for any strictly positive $i$.

\textbf{Note:} Like Exercise~\ref{exo:i-plus-omega}, this project corresponds to the [in]equalities $i+\omega=\omega<\omega+i$, for any natural number $i$.
\end{project}
